DeepSphere: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2019-03-04 rebuttal.tex

Your suggestion however made us realize that figure A.12 was not ideal in comparing the eigenvectors to the spherical harmonics.
As such, we replaced it with another that we hope is clearer.
We also moved Figure A.12 in the correct subsection.

\subsection{}
\begin{mdframed}[style=comment]
In Appendix C. is there a connection between $t$ and $\sigma$ that you can make, or do you just fit them to be similar? If you just fit them to be similar I'm not sure where the relative differences come from. If they are related, however, then the relative differences make sense, but I can't see what the connection is.
\end{mdframed}

In the current version of the manuscript and the code, we simply fitted a few $t$ to match the different $\sigma$.
In theory, there should be a connection between the two values providing the graph Laplacian has converged toward the Laplace Beltrami operator.
Again, this is left for a future contribution.

\subsection{}
\begin{mdframed}[style=comment]
A question that I would like to know personally, are you thinking about a future upgrade to non-radial kernels?
\end{mdframed}

We thought about it but are not sure that it would be beneficial.
%The main difficulty is that a graph is not intrinsically oriented.
%However, as the graph framework we are using only works with radial filters, it is not a simple question.
%A simple trick to make the network sensitive to direction is to add a per-channel fully connected layer.
%We are currently investigating other potential graph techniques that would lead to non-radial kernels.

@@

\begin{mdframed}[style=comment]
You change a lot between ``node'', ``vertex'' and ``pixel''. Could you stick to one of these? I think that ``vertex'' or ``pixel'' makes the most sense (``pixel'' due to the HEALPix pixelisation of the maps or vertex because of the use of the $v$ notation). Node is quite confusing in several places because there is an inherent connection between node and neuron in ML literature, and since there is swapping between the three different terms it's a little hard to keep track.
\end{mdframed}

We agree that using different terms for the same notion can confuse readers.
While ``node'' and ``vertex'' are synonyms in referring to the elements of a graph, a ``pixel'' is a different concept referring to a point of the (spherical) sampling.
A pixel can be represented by a vertex, but they are not the same.
As such, we decided to replace all occurrences of ``node'' with ``vertex'' but keep the two concepts of ``vertex'' and ``pixel'' separate.

% \nati{What do you think? This avoid repetition. But we could be more consistent...}
% \TK{Agreed. Do you want to make the change @nati?}
% \mdeff{Agreed. Node is the same as vertex. Pixel is not necessarily.}

\begin{mdframed}[style=comment]
You change between math font and text font for the names of your layers when inside and outside of equations. It would look a lot neater sticking with one choice. (Sorry, that seems quite petty and I don't mean it to be).
\end{mdframed}

We have made the paper consistent by using a math font for layer names.
%\nati{@all, when you read the paper, please check that I did not forget some of them. Every layer has been changed to math symbols as we use them like function. For example, SM becomes $SM$.}
%\mdeff{Agreed. I checked and fixed one missing.}

\begin{mdframed}[style=comment]
In Appendix C. you talk about Kroneker a lot, but earlier you talk about Kroneker $\delta$ (which is it's correct name). It's probably worth sticking with the full name.
\end{mdframed}

We have modified the manuscript according to the suggestion.

\begin{mdframed}[style=comment]
Sky maps are rotation invariant: rotating maps on the sphere doesn’t change their interpretation, as only the statistics of the maps are relevant.
- I think that you mean that rotating maps on the sphere doesn't change their interpretation *when* only the statistics of the maps are relevant. Say you wanted to compare the NGC against the SGC, then rotating the map would obviously change the results.
\end{mdframed}

True.
Equivariance is desired in such a case (rather than invariance).
We clarified the sentence.

@@

- It should be "These" and not "This". "These kind of maps can be created using the gravitational lensing technique [see 29, for review]"
\end{mdframed}

Thank you for spotting this mistake. We updated the manuscript.

\begin{mdframed}[style=comment]
A CNN is composed of the following main building blocks [31]: (i) a convolution, (ii) a non-linearity, (iii) a down-sampling operation, (iv) a pooling operation, and (v), optionally, normalization.

- I think that this is generalising a CNN a bit too much. In my mind (and in my personal uses of CNNs) steps (iii) and (iv) are not always necessary either. Perhaps you want to say that you wish to tackle common tasks which often arise in CNNs: i) convolution, (ii) non-linearity, (iii) down-sampling operation, (iv) pooling operation, and (v), optionally, normalisation.
\end{mdframed}

We agree that (iii) and (iv) are optional and updated the sentence accordingly.

@@

 - What do you mean by "line"? Is it a row or a column or something else which I've misunderstood?
\end{mdframed}

We mean ``column'' and have updated the manuscript.

\begin{mdframed}[style=comment]
... where $\tilde{\bf{L}}= \frac{2}{\lambda_{max}}\bf{L}-\bf{I}=-\frac{2}{\lambda_{max}}\bf{D}^{-1/2}\bf{W}\bf{D}^{-1/2}$ is the rescaled Laplacian with eigenvalues $\tilde{\Lambda}$ in [-1, 1].

 - Could you put the equation in its own 2 line align environment to make it easier to read?
\end{mdframed}

Inspired by the reviewer suggestion, we changed the layout of that equation.

@@

- It should be "such that" not "such as". "Given a map $\bf{x}\in\mathbb{R}^{N_{pix}}$, pooling defines $\bf{y}\in\mathbb{R}^{N'_{pix}}$ such that"
\end{mdframed}

Thank you for spotting this mistake. We have corrected the manuscript.

\begin{mdframed}[style=comment]
... where $f$ is a function which operates on sets (possibly of varying sizes) and $N_{pix}/N'_{pix}$ is the down-sampling factor, which for HEALPix is $|\mathcal{C}(i)| = N_{pix}/N'_{pix} = (N_{side} / N'_{side})^2 = 4^p$.

- Can you explain what $p$ is and it would probably be worth splitting this equation into a multi-line align environment for clarity.
\end{mdframed}

$p$ was introduced to highlight the fact that the coarsening factor is a power of 4 by construction of HEALPix.
It is defined as $p=\log_2(N_{side} / N'_{side})$.
We have updated the manuscript with this clarification and with an equation environment.

@@

- There is just a little mix up in this sentence, maybe a copy and paste accident.
\end{mdframed}

Thanks for spotting it. We have fixed this mistake.

\begin{mdframed}[style=comment]
The cost (or loss) function $C(\bf{Y},\bar{\bf{Y}}) = C(NN_\theta(\bf{X}),\bar{\bf{Y}})$ measures how good the prediction $\bf{Y}$ is for sample $\bf{X}$, given the ground truth $\bar{\bf{Y}}$.

- This is true for supervised learning only and should be stated.
\end{mdframed}

We do not think it is necessary to specify that this is true for supervised learning only.
The phrase ``ground truth'' should be sufficient to indicate that.
%This cost cannot be computed in an unsupervised setting anyway.
% \nati{In an unsupervised setting, this can just not be computed... Specifying it seems redundant to me.}
% \todo{To check: @michael}
% \mdeff{Agreed. The whole paper is about supervized learning anyway.}

@@

\begin{mdframed}[style=comment]
For global prediction, the cost is as if $N_{pix} = 1$.

- I think this should be "For global prediction $N_{pix} = 1$."
\end{mdframed}

We changed the text to:
\begin{mdframed}[style=manuscript]
	For global prediction, we have $N_{pix} = 1$.
\end{mdframed}

%\todo{To check: @michael}
%\mdeff{Agreed.}

@@

- This should be "We emphasise that the cost function and the SM layer are the sole differences between a neural network engineered for classification or regression."
\end{mdframed}

We followed the suggestion.

\begin{mdframed}[style=comment]
The goal of learning is to find the parameters $\theta$ of the neural network that minimize the risk $R(\theta) = E\left[C\left(NN_\theta(\bf{X}),\bar{\bf{Y}}\right)\right]$.

- It is the goal of training, not of learning (in common parlance anyway). Also, you should say that E[] is the expectation rather than leaving people to guess according to the next sentence.
\end{mdframed}

% According to us, the goal of training is to minimize the empirical risk, which does not contain the expectation.
% On the contrary, the goal of learning is to minimize the expected risk, i.e., we additionally do not want to overfit the training set.
% Hence we left ``learning'' in the text.
% Nevertheless, we specified the expectation operator.
% \nati{@Michael, please check this one carefully, also in the text, I am not sure my notation is correct}
% \mdeff{Debatable. I can see overfitting as an anti-goal of training. Doesn't matter much to me. Agreeing with him is simpler. Hence:}
We followed the suggestions.

@@

\begin{mdframed}[style=comment]
The optimization is performed by computing an error gradient w.r.t. all the parameters by back-propagation and updating them with a form of stochastic gradient descent (SGD):

- This sentence is just a bit turned upside-down, it should be "The optimisation is performed by computing an error gradient w.r.t. all the parameters and updating each parameter via back propagation using a form of stochastic gradient descent (SGD):"
\end{mdframed}

% \todo{To check: @michael, \nati{again I disagree with the reviewer}}
% \mdeff{Agree with Nathanaël.}
We are not sure, we understand the reviewer.
Back-propagation is a technique to compute gradients, not to update the parameters.
The latter is done with SGD.
We believe that the original formulation is more accurate than proposition.

@@

- It should be "which makes it computationally efficient" instead of "what". (It's possibly "that" and not "which", but I'm never sure which ;))
\end{mdframed}

This mistake has been corrected.

\begin{mdframed}[style=comment]
A straightforward way to impose locality in the original domain is to impose smoothness in the spectral domain, by Heisenberg’s uncertainty principle.

- What do you mean by "by Heisenberg’s uncertainty principle." That seemed to come out of nowhere. This needs explaining further.
\end{mdframed}

We added the general idea behind the Heisenberg's uncertainty principle.
% \mdeff{I prefer to leave "by Heisenberg [...]". Readers will otherwise wonder why the recipe... I borrowed the text from your below justification.}

% The link with the Heisenberg's uncertainty principle does exist but is too complex to explain shortly.
% We decided to remove ``by Heisenberg’s uncertainty principle'' and keep the rest of the sentence as a general Fourier analysis recipe.

@@

- You mention your method as part of the "above methods", but then you go on to say that using graphs does allow you to accelerate the method when data is only on part of the sphere.
\end{mdframed}

Indeed.
We corrected the text.

\begin{mdframed}[style=comment]
By interwinding graph convolutional layers and recurrent layers [65], they can for example model structured time series such as traffic on road networks [66], or recursively complete matrices for recommendation [67].

- I'm not sure what interwinding is, I guess you mean by making GC recurrent, or do you mean using GC and then RL separately? Either way there should be commas around "for example".
\end{mdframed}

Thanks for spotting this.
We added the necessary commas and changed ``interwinding'' for ``combining''.

@@

\begin{mdframed}[style=comment]
To prevent the cosmological models to be distinguished by their power spectra alone, the maps have been smoothed with a Gaussian kernel of radius 3 arcmins to remove high frequencies ($\ell> 1000$ ).

- This should be "To prevent the cosmological models from being distinguished by their power spectra alone the maps have been smoothed with a Gaussian kernel of radius 3 arcmins to remove high frequencies ($\ell> 1000$ ).
\end{mdframed}

We have corrected this formulation according to the reviewer suggestion.

@@

\todo{Assign: @all}
% \nati{The problem is that random filters are picky as well and look very similar. Should we say that? I do not think a colorbar is necessary since there are numbered axes on the top plots. Do you agree?}
% \TK{Added sentence}

We decided not to add a colorbar as scale information is already present in the top plot of the figure.
We added a small explanation for the peak structure
\begin{mdframed}[style=manuscript]
The structure in the filters resembles peaks, which is not unexpected, given that the convergence maps largely consist of concentrated clumps.
\end{mdframed}

\begin{mdframed}[style=comment]
The fact that a graph representation of the disretised sphere enables an efficient convolution relaxes the iso-latitude constraint on the design of sampling schemes who aim to enable fast convolutions.

- It should be "discretised" and also "who" should be "which" (or "that", I'm not actually sure myself)
\end{mdframed}

We followed the reviewer suggestion (and we went for ``which'').
% \todo{Assign: @tomek -> \nati{I corrected it with "which". Do you agree? }}
% \TK{Sounds good to me.}

### 2019-03-04 scnn.tex
comment 2.14 (details) part 3

\nati{The goal of learning is to find the parameters $\theta$ of the neural network that minimize the risk $R(\theta) = \esp \left[ C \left( NN_\theta(\X), \bar \Y \right) \right]$, where $\esp$ is the expectation over the joint distribution $(\X, \bar \Y)$.}
In general, that expectation cannot be computed as the data distribution is unknown. We can however minimize an approximation, the empirical risk over the training set $\left\{ \left( \X_i, \bar \Y_i \right) \right\}_{i=1}^{N_{samples}}$:
\begin{equation*}
	\hat{\theta} = \argmin_\theta \sum_{i=1}^{N_{samples}} C \left(NN_\theta(\X_i), \bar \Y_i \right).
\end{equation*}
The optimization is performed by computing an error gradient w.r.t.\ all the parameters by back-propagation and updating them with a form of stochastic gradient descent (SGD):
\begin{equation*}
	\theta \leftarrow \theta - \frac{\eta}{|\B|} \sum_{i \in \B} \frac{\partial C \left( NN_\theta(\X_i), \bar \Y_i \right)}{\partial \theta} ,
\end{equation*}
where $\eta$ is the learning rate, and $\B$ is the set of indices in a mini-batch. Batches are used instead of single samples to gain speed by exploiting the parallelism afforded by modern computing platforms.

@@

While defining the convolution in the spectral domain avoids all sampling issues, filters so defined are not naturally localized in the original domain.
Localization is desired for the transformation to be stable to local deformation \citep{mallat2012scattering}, and most interactions in the data are local anyway.
A straightforward way to impose locality in the original domain is to impose smoothness in the spectral domain.
% , by Heisenberg's uncertainty principle.
A more elegant approach is to define filters that are provably localized.
The filters defined in \eqnref{graph_convolution_monomial} and \eqnref{graph_convolution_cheby}, by being polynomials of the Laplacian, are of this kind.

\nati{All the presented methods, but our, cannot be easily accelerated when the data lies on a part of the sphere only.}
That is an important use case in cosmology as measurements are often partial, i.e., whole sky maps are rare.
One could still fill the unseen part of the sphere with zeros, and avoid computing empty integrals.
It is, however, not straightforward to identify empty space, and computations would still be wasted (for example on a ring that mostly contains zeros but a few measurements).
With graphs, however, computations are only performed for used pixels.
While it results in some distortions due to border effects (see \figref{border_effects} and \ref{sec:border_effects}), these can be mitigated by padding with zeros a small area around the measurements.

>>>>

The goal of training is to find the parameters $\theta$ of the neural network that minimize the risk $R(\theta) = \esp \left[ C \left( NN_\theta(\X), \bar \Y \right) \right]$, where $\esp$ is the expectation over the joint distribution $(\X, \bar \Y)$.
In general, that expectation cannot be computed as the data distribution is unknown. We can however minimize an approximation, the empirical risk over the training set $\left\{ \left( \X_i, \bar \Y_i \right) \right\}_{i=1}^{N_{samples}}$:
\begin{equation*}
	\hat{\theta} = \argmin_\theta \sum_{i=1}^{N_{samples}} C \left(NN_\theta(\X_i), \bar \Y_i \right).
\end{equation*}
The optimization is performed by computing an error gradient w.r.t.\ all the parameters by back-propagation and updating them with a form of stochastic gradient descent (SGD):
\begin{equation*}
	\theta \leftarrow \theta - \frac{\eta}{|\B|} \sum_{i \in \B} \frac{\partial C \left( NN_\theta(\X_i), \bar \Y_i \right)}{\partial \theta} ,
\end{equation*}
where $\eta$ is the learning rate, and $\B$ is the set of indices in a mini-batch. Batches are used instead of single samples to gain speed by exploiting the parallelism afforded by modern computing platforms.

@@

While defining the convolution in the spectral domain avoids all sampling issues, filters so defined are not naturally localized in the original domain.
Localization is desired for the transformation to be stable to local deformation \citep{mallat2012scattering}, and most interactions in the data are local anyway.
A straightforward way to impose locality in the original domain is to impose smoothness in the spectral domain, by Heisenberg's uncertainty principle.\footnote{Heisenberg's uncertainty principle states that a filter cannot be arbitrarily concentrated in one domain without being de-concentrated in the other.}
A more elegant approach is to define filters that are provably localized.
The filters defined in \eqnref{graph_convolution_monomial} and \eqnref{graph_convolution_cheby}, by being polynomials of the Laplacian, are of this kind.

All the presented 2D and spherical CNNs cannot be easily accelerated when the data lies on a part of the sphere only.
That is an important use case in cosmology as measurements are often partial, i.e., whole sky maps are rare.
One could still fill the unseen part of the sphere with zeros, and avoid computing empty integrals.
It is, however, not straightforward to identify empty space, and computations would still be wasted (for example on a ring that mostly contains zeros but a few measurements).
With graphs, however, computations are only performed for used pixels.
While it results in some distortions due to border effects (see \figref{border_effects} and \ref{sec:border_effects}), these can be mitigated by padding with zeros a small area around the measurements.
